\documentclass[12pt, a4paper]{article}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{physics}
\usepackage{array}
\usepackage{booktabs}
\usepackage{enumitem}

\graphicspath{ {./images/} }

\title{\Huge{Personal Learning Objectives} }
\author{Dylan Duunk \\ \textit{(0948392)}}
\date{\today}

\begin{document}

\maketitle

\noindent
In this document, I will describe my personal learning objectives.

\section*{Personal learning objectives}

\begin{description}[align=left]
    \item[3D Modeling] For the prototyping process is 3d modeling a very usefull skill to have.
                       I want to improve my 3d modeling skills by making use of an advanced CAD program like Fusion 360.
                       Fusion 360 is quite difficult program to use without any knowledge, but can be a very usefull tool.
                       For example, the functions that Fusion 360 offers make the designing of complex shapes a lot easier.
                       This can be a chore in simpler CAD programs like Tinkercad.
    \item[Version Control] Version control can be a very handy tool for development.
                           I want to learn how to make efficient use of version control and make it a habit to use version control.
    \item[Prototyping] I want to improve my ability to efficiently prototype by designing multiple iterations to make create a fully-fledged product. 
\end{description}   

\end{document}